Fast Sorting on Modern Computers

### 2005-05-31 paper/docs/merge.tex
more fixes

A disadvantage of this method is that if an array has slightly more than $2^x$
keys, an entire extra merge step would be required, which would considerably
slow the algorithm. This problem is shared by all other versions of mergesort
considered here, except algorithm N. However, since this project uses exact
powers of two as set sizes, this problem does not affect the results. LaMarca,
however, used set sizes such as 4096000, which at times would suffer from this
type of problem.

@@

Finally, the inner loop is \n{unrolled}\footnote{Unrolling a loop means
executing several steps of the loop between iterations, reducing the number of
iterations, and lowering the loop overhead, as well as allowing for better
scheduling of the instructions.}.  There are actually two inner loops, and they
are both unrolled 8 times. The compiler is also set to unroll loops. However,
the observed difference between unrolling manually and compiler unrolling is up
to 10\% of instruction count, so manual unrolling is used.

@@

>>>>

A disadvantage of this method is that if an array has slightly more than $2^x$
keys, an entire extra merge step would be required, which would considerably
slow the algorithm. This problem is shared by all other versions of mergesort
considered here, except algorithm N. However, since our tests use exact
powers of two as set sizes, this problem does not affect them. LaMarca,
however, used set sizes such as 4096000, which at times would suffer from this
type of problem.

@@

Finally, the inner loop is \n{unrolled}\footnote{Unrolling a loop means
executing several steps of the loop between iterations and reducing the number
of iterations, which lowers the loop overhead and allows for better scheduling
of the instructions.}. There are actually two inner loops, and they are both
unrolled 8 times. The compiler is also set to unroll loops. However, the
observed difference between unrolling manually and compiler unrolling is up to
10\% of instruction count, so manual unrolling is used.

@@

%TODO what does this formula mean. look up LaMarcas paper
